R for Clinical Study Reports and Submission

### 2021-11-01 submission-environment.Rmd

In the previous chapter, we have generated instructions to manually
create the running environments for reproducing the A&R deliverables.

In this chapter, we will focus on automating the creation of
the R environments with R code, to accelerate the dry run testing process,
simplify the ADRG instructions, and make it easy to recreate
different environment settings with reproducible analysis results.

@@

The helper functions `version_*()` and `snapshot_*()` could assist you
to determine specific versions of R and Rtools that are currently available,
besides generating and verifying the snapshot repo links.

@@

Go to the working directory created above, double click the .Rproj file
to open the project in RStudio. Follow the instructions to select the
project-specific R version then restart RStudio. If successful,
the R version and package repo should be printed as defined above.

>>>>

In the previous chapter, we generated instructions to manually
create the running environments for reproducing the A&R deliverables.

In this chapter, we will focus on automating the creation of
the R environments with R code to accelerate the dry run testing process,
simplifying the ADRG instructions, and making it easy to recreate
different environment settings with reproducible analysis results.

@@

The helper functions `version_*()` and `snapshot_*()` could assist you
in determining specific versions of R and Rtools that are currently available,
besides generating and verifying the snapshot repo links.

@@

Go to the working directory created above, double click the .Rproj file
to open the project in RStudio. Follow the instructions to select the
project-specific R version, then restart RStudio. If successful,
the R version and package repo should be printed as defined above.

### 2021-11-01 tlf-ae-spec.Rmd

In this way, let's focus on the analysis script for two advanced
features for table layout.

-   group content: AE can be summarized in multiple nested layers. (e.g.
    by system organ class (SOC, `AESOC`) and specific AE term
    (`AEDECOD`))
-   pagenization: there are many AE terms that can not be covered in one
    page. Column headers and SOC information need to be repeated on
    every page.

@@

We can also customize the text format by providing a matrix that has the
same dimension as the input dataset (i.e. `tbl_ae_spec`). In the code
below, we illustrate how to display **bold** text for group headers to
highlight the nested structure of the table layout.

>>>>

In this way, let's focus on the analysis script for two advanced
features for a table layout.

- group content: AE can be summarized in multiple nested layers.
  (e.g., by system organ class (SOC, `AESOC`) and specific AE term
  (`AEDECOD`))
- pagenization: there are many AE terms that can not be covered in one
  page. Column headers and SOC information need to be repeated on
  every page.

@@

We can also customize the text format by providing a matrix that has the
same dimension as the input dataset (i.e., `tbl_ae_spec`). In the code
below, we illustrate how to display **bold** text for group headers to
highlight the nested structure of the table layout.
